\documentclass[11pt]{article}

%====================
% Basic setup
%====================
\usepackage[left=0.5in, right=0.5in, top=0.5in, bottom=0.5in]{geometry}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{setspace}

\hypersetup{
    colorlinks=true,
    urlcolor=black
}

\setlist[itemize]{noitemsep, topsep=2pt}

\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}
\pagenumbering{gobble}

%====================
% Section formatting
%====================
\titleformat{\section}
  {\large\bfseries}
  {}
  {0pt}
  {}
  [\vspace{2pt}\titlerule]

%====================
% Document
%====================
\begin{document}

%====================
% Header
%====================
{\LARGE \textbf{Angel Fernando Borquez Guerrero}} \\
\vspace{-0.4cm}
\par \href{https://www.linkedin.com/in/fernandoborquez/}{LinkedIn} \quad | \quad
\href{https://github.com/FernyBoy}{GitHub} \quad | \quad
\href{mailto:fernandoborquez215@icloud.com}{fernandoborquez215@icloud.com} \quad | \quad
+52 633 100 5991 \\
Hermosillo, Sonora.

\vspace{-0.3cm}

%====================
% Education
%====================
\section*{Education}
\vspace{-0.3cm}
\textbf{Universidad de Sonora} \hfill GPA: 90\%\\
Bachelor of Science in Computer Science \hfill \textbf{August 2023 -- Present}

\vspace{-0.35cm}

%====================
% Professional Experience
%====================
\section*{Professional Experience}
\vspace{-0.3cm}
\textbf{ACARUS — Supercomputing Area} \hfill Supervisor: Dra. María del Carmen Heras Sánchez\\
Professional Intern \hfill \textbf{September 2025 -- Present}
\vspace{-0.3cm}
\begin{itemize}[leftmargin=*]
    \item Part of a development team building a specialized forum for users of \textit{Yuca}, the university HPC system.
    \item Implemented core features including posts, direct messaging, and service request workflows to support the HPC user community.
\end{itemize}

\vspace{-0.35cm}

%====================
% Research Experience
%====================
\section*{Research Experience}
\vspace{-0.3cm}
\textbf{University of Guadalajara} \hfill Supervisor: Dr. Rafael Morales Gamboa \\
Research Intern \hfill \textbf{June -- July 2025}
\vspace{-0.3cm}
\begin{itemize}[leftmargin=*]
    \item Extended and evaluated an Entropic Associative Memory (EAM) model through large-scale experiments combining neural representations and probabilistic memory.
    \item Refactored the data pipeline and experimental framework to support scalable datasets, dynamic class selection, and controlled novelty detection experiments.
    \item Retrained perceptual neural networks and designed evaluation protocols to analyze memory recall, rejection behavior, and robustness.
\end{itemize}

\vspace{-0.35cm}

%====================
% Competitions & Projects
%====================
\section*{Competitions \& Projects}
\vspace{-0.3cm}
\textbf{NASA Space Apps Challenge (2024)} \hfill Project: Voyager CXXV\\
Project Co-Lead \hfill \textbf{October 2024}
\vspace{-0.3cm}
\begin{itemize}[leftmargin=*]
    \item Co-led the development of a geospatial simulation tool to evaluate the impact of urban green areas on temperature and air quality.
    \item Designed interactive spatial visualizations and coordinated technical integration within the team.
\end{itemize}


\textbf{TE AI CUP (2025)} \hfill Project: AI Generated Machine Downtime Insights\\
UI Developer \hfill \textbf{January -- May 2025}
\vspace{-0.3cm}
\begin{itemize}[leftmargin=*]
    \item Developed the user interface for an AI-based industrial downtime analysis tool, focusing on clear visualization of patterns, anomalies, and clustering results derived from machine time-series data.
\end{itemize}

\textbf{NASA Space Apps Challenge (2025)} \hfill Project: Endurance CXXV\\
Project Co-Lead \hfill \textbf{October 2025}
\vspace{-0.3cm}
\begin{itemize}[leftmargin=*]
    \item Co-led the development of an educational weather application focused on climate awareness for children.
    \item Developed frontend, backend, and UI components with emphasis on accessibility and usability.
\end{itemize}


\textbf{1st Place Winner -- MICAI 2025 MeDA Challenge} \hfill \textbf{October 2025}
\vspace{-0.3cm}
\begin{itemize}[leftmargin=*]
    \item Contributed to a 1st Place victory in a national competition on Medical Domain Adaptation using Self-Supervised Learning (SSL), leading to an invitation to publish in a journal special issue.
    \item Supported the project through dataset structuring, scientific writing, and development of presentation and visual assets.
\end{itemize}

\vspace{-0.35cm}

%====================
% Technical Skills
%====================
\section*{Technical Skills}
\vspace{-0.3cm}
\textbf{Programming:} Python, C++, Java, SQL, JavaScript, TypeScript \\
\textbf{Web:} HTML, CSS, SASS, Vue.js, Django, NPM \\
\textbf{Systems:} Linux (Arch), HPC, Virtual Machines, Proxmox VE, VirtualBox \\
\textbf{Tools:} Git, GitHub, Jupyter, Google Colab, LaTeX, GIS

\end{document}
